Manuscript

### 2018-11-14 manuscript.Rmd

## Pearson correlation by lineage
```{r}
PearsonByLineage <- function(lin, dataset) {
  use_data <- filter(dataset, group_general_lineage_name == lin)
  use_data <- filter(use_data, !is.na(RPKM))
  use_data_summ <- use_data %>% count(Drug_Gene)
  use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
  use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
  if(nrow(use_data_filt) > 0) {
    pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
    pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
    pearson_res$group_general_lineage_name <- lin
    pearson_res$Pearson_Corr_Abs <- abs(pearson_res$Pearson_Corr)
    pearson_res$Pearson_Corr_Sign <- ifelse(sign(pearson_res$Pearson_Corr) == 1, "+",
                                            ifelse(sign(pearson_res$Pearson_Corr) == -1, "-", "0"))
    return(pearson_res)
  }
}
```

@@

## Make G2P lineage gene expression plotly
```{r}
GexpPlotlyByLineage <- function(lineage) {
  use_data <- filter(signif_pearson_all_lin, group_general_lineage_name == lineage)
  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
  use_data$Pearson_Pvalue <- paste0(round(use_data$Pearson_Pval, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
  ticker <- 0

  use_data_ccle <- filter(use_data, Dataset == "CCLE")
  use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
  ccle_lin_ttest <- data.frame(statistic = NA,
                                 parameter =  NA,
                                 p.value = NA)
  if(nrow(use_data_ccle_summ) <= 1) {
    ccle_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn < 2) { ccle_ttest_res <-  NA }
  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
    ccle_lin_ttest <- t.test(use_data_ccle$Pearson_Corr_Abs ~ use_data_ccle$InG2P)
    ccle_ttest_res <- paste0("t = ", round(ccle_lin_ttest$statistic, 3), ", df = ", round(ccle_lin_ttest$parameter, 3), ", p = ", round(ccle_lin_ttest$p.value, 3))
  }

  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
  use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
  ctrp_lin_ttest <- data.frame(statistic = NA,
                                 parameter =  NA,
                                 p.value = NA)
  if(nrow(use_data_ctrp_summ) <= 1) {
    ctrp_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn < 2) { ctrp_ttest_res <-  NA }
  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
    ctrp_lin_ttest <- t.test(use_data_ctrp$Pearson_Corr_Abs ~ use_data_ctrp$InG2P)
    ctrp_ttest_res <- paste0("t = ", round(ctrp_lin_ttest$statistic, 3), ", df = ", round(ctrp_lin_ttest$parameter, 3), ", p = ", round(ctrp_lin_ttest$p.value, 3))
  }

  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
  gdsc_lin_ttest <- data.frame(statistic = NA,
                                 parameter =  NA,
                                 p.value = NA)
  if(nrow(use_data_gdsc_summ) <= 1) {
    gdsc_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_ttest_res <-  NA }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_lin_ttest <- t.test(use_data_gdsc$Pearson_Corr_Abs ~ use_data_gdsc$InG2P)
    gdsc_ttest_res <- paste0("t = ", round(gdsc_lin_ttest$statistic, 3), ", df = ", round(gdsc_lin_ttest$parameter, 3), ", p = ", round(gdsc_lin_ttest$p.value, 3))
  }

  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                          Test_Results_p = c(ccle_ttest_res, ctrp_ttest_res, gdsc_ttest_res),
                          t_statistic = c(round(ccle_lin_ttest$statistic, 3), round(ctrp_lin_ttest$statistic, 3), round(gdsc_lin_ttest$statistic, 3)),
                          df = c(round(ccle_lin_ttest$parameter, 3), round(ctrp_lin_ttest$parameter, 3), round(gdsc_lin_ttest$parameter, 3)),
                          p_value = c(round(ccle_lin_ttest$p.value, 3), round(ctrp_lin_ttest$p.value, 3), round(gdsc_lin_ttest$p.value, 3)),
                          group_general_lineage_name = lineage)

  plot_point <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    scale_y_continuous(breaks = pretty_breaks()) +
    geom_point(mapping = aes(label = Pearson_Pvalue, color = InG2P, fill = InG2P, shape = Pearson_Corr_Sign, x = Pearson_Corr_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
    scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 1) +
    labs(y = "Number of level A G2P associations") +
    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

  plot_box <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5) +
    geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    coord_flip() +
    labs(x = "Level A G2P\nassociation") +
    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = lineage, margin = list(t = 75, l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

  saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/plotlys_pearson_by_lineage/", lineage, "_g2p_evidence_pearson_plotly.html"))
  return(summ_text)
}
```

@@

## Drugscreen: Mutation status G2P evidence

@@

@@

@@

g2p_druggene_all_p_summ_plot <- cowplot::plot_grid(plot_p_box,
                   plot_p_point,
                   nrow = 2,
                   rel_heights = c(1.5, 4))
g2p_druggene_all_p_summ_plot
# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.png", g2p_druggene_all_p_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

@@

plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

saveWidgetFix(widget = plot, file = "./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.html")
```

>>>>

## Pearson correlation by lineage
```{r}
PearsonByLineage <- function(lin, dataset, variable) {
  use_data <- filter(dataset, group_general_lineage_name == lin)
  if(variable == "GE") {
    use_data <- filter(use_data, !is.na(RPKM))
    use_data_summ <- use_data %>% count(Drug_Gene)
    use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
    use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
    if(nrow(use_data_filt) > 0) {
      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
      pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
      pearson_res$group_general_lineage_name <- lin
      pearson_res$Pearson_GE_Abs <- abs(pearson_res$Pearson_Corr_GE)
      pearson_res$Pearson_GE_Sign <- ifelse(sign(pearson_res$Pearson_Corr_GE) == 1, "+",
                                              ifelse(sign(pearson_res$Pearson_Corr_GE) == -1, "-", "0"))
      return(pearson_res)
    }
  }
  else if(variable == "CN") {
    use_data <- filter(use_data, !is.na(Copy_Number))
    use_data_summ <- use_data %>% count(Drug_Gene)
    use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
    use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
    if(nrow(use_data_filt) > 0) {
      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$p.value)
      pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
      pearson_res$group_general_lineage_name <- lin
      pearson_res$Pearson_CN_Abs <- abs(pearson_res$Pearson_Corr_CN)
      pearson_res$Pearson_CN_Sign <- ifelse(sign(pearson_res$Pearson_Corr_CN) == 1, "+",
                                              ifelse(sign(pearson_res$Pearson_Corr_CN) == -1, "-", "0"))
      return(pearson_res)
    }
  }
}
```

@@

## Make G2P lineage Pearson plotlys
```{r}
PearsonPlotlyByLineage <- function(lineage) {
  print(paste0("Lineage: ", toupper(lineage)))
  use_data <- filter(signif_all_lin, group_general_lineage_name == lineage)
  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
  use_data$Pearson_GE_Label <- paste0(round(use_data$Pearson_Pval_GE, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
  use_data$Pearson_CN_Label <- paste0(round(use_data$Pearson_Pval_CN, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
  ticker_ge <- 0
  ticker_cn <- 0
  ticker <- 0

  use_data_ccle <- filter(use_data, Dataset == "CCLE")
  use_data_ccle_ge_summ <- use_data_ccle[!is.na(use_data_ccle$Pearson_GE_Abs),] %>% count(InG2P)
  use_data_ccle_cn_summ <- use_data_ccle[!is.na(use_data_ccle$Pearson_CN_Abs),] %>% count(InG2P)
  ccle_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  ccle_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  if(nrow(use_data_ccle_ge_summ) <= 1) {
    ccle_ge_res <-  NA
    ticker_ge <- ticker_ge + 1
  }
  else if(use_data_ccle_ge_summ[use_data_ccle_ge_summ$InG2P == "Yes",]$nn < 2) {
    ccle_ge_res <-  NA
  }
  else if(use_data_ccle_ge_summ[use_data_ccle_ge_summ$InG2P == "Yes",]$nn >= 2) {
    ccle_ge_ttest <- t.test(use_data_ccle$Pearson_GE_Abs ~ use_data_ccle$InG2P)
    ccle_ge_res <- paste0("t = ", round(ccle_ge_ttest$statistic, 3), ", df = ", round(ccle_ge_ttest$parameter, 3), ", p = ", round(ccle_ge_ttest$p.value, 3))
  }
  if(nrow(use_data_ccle_cn_summ) <= 1) {
    ccle_cn_res <-  NA
    ticker_cn <- ticker_cn + 1
  }
  else if(use_data_ccle_cn_summ[use_data_ccle_cn_summ$InG2P == "Yes",]$nn < 2) {
    ccle_cn_res <-  NA
  }
  else if(use_data_ccle_cn_summ[use_data_ccle_cn_summ$InG2P == "Yes",]$nn >= 2) {
    ccle_cn_ttest <- t.test(use_data_ccle$Pearson_CN_Abs ~ use_data_ccle$InG2P)
    ccle_cn_res <- paste0("t = ", round(ccle_cn_ttest$statistic, 3), ", df = ", round(ccle_cn_ttest$parameter, 3), ", p = ", round(ccle_cn_ttest$p.value, 3))
  }
  print("CCLE testing: DONE")

  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
  use_data_ctrp_ge_summ <- use_data_ctrp[!is.na(use_data_ctrp$Pearson_GE_Abs),] %>% count(InG2P)
  use_data_ctrp_cn_summ <- use_data_ctrp[!is.na(use_data_ctrp$Pearson_CN_Abs),] %>% count(InG2P)
  ctrp_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  ctrp_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  if(nrow(use_data_ctrp_ge_summ) <= 1) {
    ctrp_ge_res <-  NA
    ticker_ge <- ticker_ge + 1
  }
  else if(use_data_ctrp_ge_summ[use_data_ctrp_ge_summ$InG2P == "Yes",]$nn < 2) {
    ctrp_ge_res <-  NA
  }
  else if(use_data_ctrp_ge_summ[use_data_ctrp_ge_summ$InG2P == "Yes",]$nn >= 2) {
    ctrp_ge_ttest <- t.test(use_data_ctrp$Pearson_GE_Abs ~ use_data_ctrp$InG2P)
    ctrp_ge_res <- paste0("t = ", round(ctrp_ge_ttest$statistic, 3), ", df = ", round(ctrp_ge_ttest$parameter, 3), ", p = ", round(ctrp_ge_ttest$p.value, 3))
  }
  if(nrow(use_data_ctrp_cn_summ) <= 1) {
    ctrp_cn_res <-  NA
    ticker_cn <- ticker_cn + 1
  }
  else if(use_data_ctrp_cn_summ[use_data_ctrp_cn_summ$InG2P == "Yes",]$nn < 2) {
    ctrp_cn_res <-  NA
  }
  else if(use_data_ctrp_cn_summ[use_data_ctrp_cn_summ$InG2P == "Yes",]$nn >= 2) {
    ctrp_cn_ttest <- t.test(use_data_ctrp$Pearson_CN_Abs ~ use_data_ctrp$InG2P)
    ctrp_cn_res <- paste0("t = ", round(ctrp_cn_ttest$statistic, 3), ", df = ", round(ctrp_cn_ttest$parameter, 3), ", p = ", round(ctrp_cn_ttest$p.value, 3))
  }
  print("CTRP testing: DONE")

  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
  use_data_gdsc_ge_summ <- use_data_gdsc[!is.na(use_data_gdsc$Pearson_GE_Abs),] %>% count(InG2P)
  use_data_gdsc_cn_summ <- use_data_gdsc[!is.na(use_data_gdsc$Pearson_CN_Abs),] %>% count(InG2P)
  gdsc_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  gdsc_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  if(nrow(use_data_gdsc_ge_summ) <= 1) {
    gdsc_ge_res <-  NA
    ticker_ge <- ticker_ge + 1
  }
  else if(use_data_gdsc_ge_summ[use_data_gdsc_ge_summ$InG2P == "Yes",]$nn < 2) {
    gdsc_ge_res <-  NA
  }
  else if(use_data_gdsc_ge_summ[use_data_gdsc_ge_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_ge_ttest <- t.test(use_data_gdsc$Pearson_GE_Abs ~ use_data_gdsc$InG2P)
    gdsc_ge_res <- paste0("t = ", round(gdsc_ge_ttest$statistic, 3), ", df = ", round(gdsc_ge_ttest$parameter, 3), ", p = ", round(gdsc_ge_ttest$p.value, 3))
  }
  if(nrow(use_data_gdsc_cn_summ) <= 1) {
    gdsc_cn_res <-  NA
    ticker_cn <- ticker_cn + 1
  }
  else if(use_data_gdsc_cn_summ[use_data_gdsc_cn_summ$InG2P == "Yes",]$nn < 2) {
    gdsc_cn_res <-  NA
  }
  else if(use_data_gdsc_cn_summ[use_data_gdsc_cn_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_cn_ttest <- t.test(use_data_gdsc$Pearson_CN_Abs ~ use_data_gdsc$InG2P)
    gdsc_cn_res <- paste0("t = ", round(gdsc_cn_ttest$statistic, 3), ", df = ", round(gdsc_cn_ttest$parameter, 3), ", p = ", round(gdsc_cn_ttest$p.value, 3))
  }
  print("GDSC testing: DONE")

  y_value_ge <- ifelse(ticker_ge == 3, 10, max(use_data$n) + 1)
  y_value_cn <- ifelse(ticker_cn == 3, 10, max(use_data$n) + 1)
  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                          Test_Results_GE = c(ccle_ge_res, ctrp_ge_res, gdsc_ge_res),
                          t_statistic_GE = c(round(ccle_ge_ttest$statistic, 3), round(ctrp_ge_ttest$statistic, 3), round(gdsc_ge_ttest$statistic, 3)),
                          df_GE = c(round(ccle_ge_ttest$parameter, 3), round(ctrp_ge_ttest$parameter, 3), round(gdsc_ge_ttest$parameter, 3)),
                          p_value_GE = c(round(ccle_ge_ttest$p.value, 3), round(ctrp_ge_ttest$p.value, 3), round(gdsc_ge_ttest$p.value, 3)),
                          Test_Results_CN = c(ccle_cn_res, ctrp_cn_res, gdsc_cn_res),
                          t_statistic_CN = c(round(ccle_cn_ttest$statistic, 3), round(ctrp_cn_ttest$statistic, 3), round(gdsc_cn_ttest$statistic, 3)),
                          df_CN = c(round(ccle_cn_ttest$parameter, 3), round(ctrp_cn_ttest$parameter, 3), round(gdsc_cn_ttest$parameter, 3)),
                          p_value_CN = c(round(ccle_cn_ttest$p.value, 3), round(ctrp_cn_ttest$p.value, 3), round(gdsc_cn_ttest$p.value, 3)),
                          group_general_lineage_name = lineage)

  ## Gene expression
  if(sum(!is.na(use_data$Pearson_GE_Abs)) > 0) {
    plot_ge_point <- ggplot(data = use_data) +
      facet_wrap(~ Dataset, drop = FALSE) +
      scale_y_continuous(breaks = pretty_breaks()) +
      geom_point(mapping = aes(label = Pearson_GE_Label, color = InG2P, fill = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
      scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_ge, label = Test_Results_GE), nudge_y = 1) +
      labs(y = "Number of level A G2P associations") +
      theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
    plot_ge_box <- ggplot(data = use_data) +
      facet_wrap(~ Dataset, drop = FALSE) +
      geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
      geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      coord_flip() +
      theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
    plot_ge <- subplot(plot_ge_box, plot_ge_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>%
               layout(title = lineage, margin = list(t = 75, l = 75),
                      xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"),
                      yaxis = list(title = "In G2P?", domain = c(0.8, 1)),
                      yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
    saveWidgetFix(widget = plot_ge, file = paste0("./plots_18Q3/manuscript/plotlys_ge_by_lineage/", lineage, "_ge_plotly.html"))
    print("Gene expression plotly: DONE")
  }
  else if(sum(!is.na(use_data$Pearson_GE_Abs)) == 0) { print("Gene expression plotly: None") }

  ## Copy number
  if(sum(!is.na(use_data$Pearson_CN_Abs)) > 0) {
    plot_cn_point <- ggplot(data = use_data) +
      facet_wrap(~ Dataset, drop = FALSE) +
      scale_y_continuous(breaks = pretty_breaks()) +
      geom_point(mapping = aes(label = Pearson_CN_Label, color = InG2P, fill = InG2P, shape = Pearson_CN_Sign, x = Pearson_CN_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
      scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_cn, label = Test_Results_CN), nudge_y = 1) +
      labs(y = "Number of level A G2P associations") +
      theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
    plot_cn_box <- ggplot(data = use_data) +
      facet_wrap(~ Dataset, drop = FALSE) +
      geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
      geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      coord_flip() +
      theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
    plot_cn <- subplot(plot_cn_box, plot_cn_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>%
               layout(title = lineage, margin = list(t = 75, l = 75),
                      xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"),
                      yaxis = list(title = "In G2P?", domain = c(0.8, 1)),
                      yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
    saveWidgetFix(widget = plot_cn, file = paste0("./plots_18Q3/manuscript/plotlys_cn_by_lineage/", lineage, "_cn_plotly.html"))
    print("Copy number plotly: DONE")
  }
  else if(sum(!is.na(use_data$Pearson_CN_Abs)) == 0) { print("Copy number plotly: None") }

  return(summ_text)
}
```

@@

## Drugscreen: G2P evidence

@@

#### Mutation status

@@

plot_p_box <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  coord_flip() +
  labs(x = "In G2P?") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

@@

g2p_druggene_mut_plot <- cowplot::plot_grid(plot_p_box,
                   plot_p_point,
                   nrow = 2,
                   rel_heights = c(1, 4))
g2p_druggene_mut_plot
# ggsave("./plots_18Q3/manuscript/g2p_druggene_mut_plot.png", g2p_druggene_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

@@

plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

saveWidgetFix(widget = plot, file = "./plots_18Q3/manuscript/g2p_druggene_mut_plot.html")
```

#### GE and CN

```{r}
ccle_pearson_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$p.value)
ccle_pearson_res <- merge(g2p_druggene_p_tally, ccle_pearson_res, by = "Drug_Gene", all.y = TRUE)
ccle_pearson_res$n <- ifelse(is.na(ccle_pearson_res$n), 0, ccle_pearson_res$n)
ccle_pearson_res$InG2P <- ifelse(ccle_pearson_res$n != 0, "Yes", "No")
ccle_pearson_res$Dataset <- "CCLE"
ccle_pearson_ttest_GE <- t.test(ccle_pearson_res$Pearson_Corr_GE ~ ccle_pearson_res$InG2P)
ccle_pearson_ttest_res_GE <- paste0("t = ", round(ccle_pearson_ttest_GE$statistic, 3), ", df = ", round(ccle_pearson_ttest_GE$parameter, 3), ", p = ", round(ccle_pearson_ttest_GE$p.value, 3))
ccle_pearson_ttest_CN <- t.test(ccle_pearson_res$Pearson_Corr_CN ~ ccle_pearson_res$InG2P)
ccle_pearson_ttest_res_CN <- paste0("t = ", round(ccle_pearson_ttest_CN$statistic, 3), ", df = ", round(ccle_pearson_ttest_CN$parameter, 3), ", p = ", round(ccle_pearson_ttest_CN$p.value, 3))

ctrp_pearson_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$p.value)
ctrp_pearson_res <- merge(g2p_druggene_p_tally, ctrp_pearson_res, by = "Drug_Gene", all.y = TRUE)
ctrp_pearson_res$n <- ifelse(is.na(ctrp_pearson_res$n), 0, ctrp_pearson_res$n)
ctrp_pearson_res$InG2P <- ifelse(ctrp_pearson_res$n != 0, "Yes", "No")
ctrp_pearson_res$Dataset <- "CTRP"
ctrp_pearson_ttest_GE <- t.test(ctrp_pearson_res$Pearson_Corr_GE ~ ctrp_pearson_res$InG2P)
ctrp_pearson_ttest_res_GE <- paste0("t = ", round(ctrp_pearson_ttest_GE$statistic, 3), ", df = ", round(ctrp_pearson_ttest_GE$parameter, 3), ", p = ", round(ctrp_pearson_ttest_GE$p.value, 3))
ctrp_pearson_ttest_CN <- t.test(ctrp_pearson_res$Pearson_Corr_CN ~ ctrp_pearson_res$InG2P)
ctrp_pearson_ttest_res_CN <- paste0("t = ", round(ctrp_pearson_ttest_CN$statistic, 3), ", df = ", round(ctrp_pearson_ttest_CN$parameter, 3), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))

gdsc_pearson_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$p.value)
gdsc_pearson_res <- merge(g2p_druggene_p_tally, gdsc_pearson_res, by = "Drug_Gene", all.y = TRUE)
gdsc_pearson_res$n <- ifelse(is.na(gdsc_pearson_res$n), 0, gdsc_pearson_res$n)
gdsc_pearson_res$InG2P <- ifelse(gdsc_pearson_res$n != 0, "Yes", "No")
gdsc_pearson_res$Dataset <- "GDSC"
gdsc_pearson_ttest_GE <- t.test(gdsc_pearson_res$Pearson_Corr_GE ~ gdsc_pearson_res$InG2P)
gdsc_pearson_ttest_res_GE <- paste0("t = ", round(gdsc_pearson_ttest_GE$statistic, 3), ", df = ", round(gdsc_pearson_ttest_GE$parameter, 3), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
gdsc_pearson_ttest_CN <- t.test(gdsc_pearson_res$Pearson_Corr_CN ~ gdsc_pearson_res$InG2P)
gdsc_pearson_ttest_res_CN <- paste0("t = ", round(gdsc_pearson_ttest_CN$statistic, 3), ", df = ", round(gdsc_pearson_ttest_CN$parameter, 3), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))

g2p_druggene_pearson <- rbind(ccle_pearson_res, ctrp_pearson_res, gdsc_pearson_res)
g2p_druggene_pearson$Pearson_GE_Abs <- abs(g2p_druggene_pearson$Pearson_Corr_GE)
g2p_druggene_pearson$Pearson_GE_Sign <- ifelse(sign(g2p_druggene_pearson$Pearson_Corr_GE) == 1, "+",
                                           ifelse(sign(g2p_druggene_pearson$Pearson_Corr_GE) == -1, "-", "0"))
g2p_druggene_pearson$Pearson_CN_Abs <- abs(g2p_druggene_pearson$Pearson_Corr_CN)
g2p_druggene_pearson$Pearson_CN_Sign <- ifelse(sign(g2p_druggene_pearson$Pearson_Corr_CN) == 1, "+",
                                           ifelse(sign(g2p_druggene_pearson$Pearson_Corr_CN) == -1, "-", "0"))
g2p_druggene_pearson_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                                        Test_Results_GE = c(ccle_pearson_ttest_res_GE, ctrp_pearson_ttest_res_GE, gdsc_pearson_ttest_res_GE),
                                        Test_Results_CN = c(ccle_pearson_ttest_res_CN, ctrp_pearson_ttest_res_CN, gdsc_pearson_ttest_res_CN))
```
